What is long-distance dispersal? And a taxonomy of dispersal events\\ \vspace{2cm}

### 2016-10-11 Manuscript/MS- What is LDD.tex
Edited Figure legends.

Dispersal is a key individual-based process influencing many life-history attributes and scaling up to population-level properties (e.g., metapopulation connectivity, \citealt{Cousens:2008aa}). In the specific case of plants, largely sessile organisms, dispersal has three basic components: 1) a distinct (sessile) source, the maternal plant producing the fruits or the paternal tree acting as a source of pollen; 2) a distance component between source and target locations; and 3) a vector actually performing the movement entailing the dispersal event. While realized dispersal also depends upon stages subsequent to dissemination (e.g., successful germination and seedling establishment) \cite{Schupp:1995}, the three previous components fully characterize the dispersal process per se. Therefore, plant movement differs in important natural history details from animal dispersal, yet both can be assessed within a common conceptual framework \citep[e.g., ][]{Nathan:2006aa}. Characteristically, animal-assisted plant dispersal has three distinct, highly integrated, components missing in the process of animal dispersal: the properties of the source (parental) plant, that mediate in the foraging of the animal vector (pollinator or frugivore), the intrinsic properties of the propagule, and the functional characteristics of the animal vector who performs the movement \citep{Nathan:2008fx}.

@@

LDD, and its variation across coexisting plant species, could also have far-reaching consequences for community assembly and forest physiognomy. Yet very few previous analyses addressed this point. Comparative information on LDD across species sharing a common environment have found strong differences in LDD potential among plants with different (e.g. Clark et al. 1999 Ecology; Martínez et al. 2008 Oecologia) or even with the same dispersal syndrome (e.g. García et al. 2016 Basic Applied Ecology).

@@

\textbf{Figure 1}. The two approaches used in analyses of dispersal processes in plants. A, the “forward” approach attempts to track the dispersal events away from the known sources, e.g., by tracking the movement patterns of frugivores as they leave fruiting plants after feeding. B, the “backward” approach  attempts to reconstruct the most likely source of a dispersed propagule by inferring the sources given the propagule delivery pattern, the fecundity of potential sources, and the dispersal function. The main technical challenge in A is to sample enough dispersal events away from the source to be able to fully characterize the tail (long-distance dispersal, LDD, events) of the dispersal function. In B, the main challenge is to have a robust sampling scheme with propagule collectors (e.g., seed traps) and a good characterization of the potential sources to derive robust estimates of the actual sources with inverse-modeling techniques.\\

\textbf{Figure 2}. Schematic representation of different types of long-distance dispersal events in relation to the geographical limits of local populations (dashed lines) and the genetic neighborhood area $N^b_e$ (grey area) of specific individual plants (squares). Dispersal events (arrows) can be classified depending on their actual incidence on propagule movement outside these spatially-explicit reference areas (Table 1). Strict-sense long-distance dispersal events ($LDD_{ss}$) just include the LDD events that disseminate propagules out of \textit{both} the population and genetic neighborhood boundaries. A, the neighborhood area is included within the geographic limits of the population, with some dispersal events potentially contributing local LDD; B, the neighborhood area is much larger than the geographic limits of the population.\\

>>>>

Dispersal is a key individual-based process influencing many life-history attributes and scaling up to population-level properties (e.g., metapopulation connectivity, \citealt{Cousens:2008aa}). In the specific case of plants, largely sessile organisms, dispersal has three basic components: 1) a distinct (sessile) source, the maternal plant producing the fruits or the paternal tree acting as a source of pollen; 2) a distance component between source and target locations; and 3) a vector actually performing the movement entailing the dispersal event. While realized dispersal also depends upon stages subsequent to dissemination \citep[e.g., successful germination and seedling establishment;][]{Schupp:1995}, the three previous components fully characterize the dispersal process per se. Therefore, plant movement differs in important natural history details from animal dispersal, yet both can be assessed within a common conceptual framework \citep[e.g., ][]{Nathan:2006aa}. Characteristically, animal-assisted plant dispersal has three distinct, highly integrated, components missing in the process of animal dispersal: the properties of the source (parental) plant, that mediate in the foraging of the animal vector (pollinator or frugivore), the intrinsic properties of the propagule, and the functional characteristics of the animal vector who performs the movement \citep{Nathan:2008fx}.

@@

LDD, and its variation across coexisting plant species, could also have far-reaching consequences for community assembly and forest physiognomy. Yet very few previous analyses address this point. Comparative information on LDD across species sharing a common environment have found strong differences in LDD potential among plants with different \citep[e.g.,][]{Clark:1999sv,Martinez:2008jx} or even with the same dispersal syndrome \citep{Garcia:2016bd}.

@@

\textbf{Figure 1}. The two approaches used in analyses of dispersal processes in plants. A, the “forward” approach attempts to track the dispersal events away from the known sources, e.g., by tracking the movement patterns of frugivores as they leave fruiting plants after feeding (i.e., the Lagrangian approach, \citep{Nathan:2003qe}). B, the “backward” approach  attempts to reconstruct the most likely source of a dispersed propagule by inferring the sources given the propagule delivery pattern, the fecundity of potential sources, and the dispersal function (i.e., the Eulerian approach). The main technical challenge in A is to sample enough dispersal events away from the source to be able to fully characterize the tail (long-distance dispersal, LDD, events) of the dispersal function. In B, the main challenge is to have a robust sampling scheme with propagule collectors (e.g., seed traps) and a good characterization of the potential sources to derive robust estimates of the actual sources with inverse-modeling techniques \citep{Nathan:2003qe}.\\

\textbf{Figure 2}. Schematic representation of different types of long-distance dispersal events in relation to the geographical limits of local populations (dashed lines) and the genetic neighborhood area $N^b_e$ (grey area) of specific individual plants (squares). Dispersal events (arrows) can be classified depending on their actual incidence on propagule movement outside these spatially-explicit reference areas (Table 1). Strict-sense long-distance dispersal events ($LDD_{ss}$) just include the LDD events that disseminate propagules out of \textit{both} the population and genetic neighborhood boundaries. A, the neighborhood area is included within the geographic limits of the population, with some dispersal events potentially contributing local LDD; B, the neighborhood area is much larger than the geographic limits of the population. Both $LDD_{ss}$ and $LDD_{loc}$ may contribute genetic novelty by moving propagules outside the $N^b_e$ area or the population limit, area or both.\\
